---
title: "Exploratory Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
We are studying how educational data highlights social injustices. Variables
such as school amenities, school funding, graduation rate, dropout rate, and 
more could demonstrate what districts are receiving disproportionately high
or low support. We will investigate how primary and secondary education data 
relates to post-secondary (post-graduation) education data.If able, we are also 
interested in analyzing how access to environmental education and outdoor spaces
impacts students post-graduation (such impacts could include belief in climate 
change). Social and environmental justice are connected because the impacts of
climate change disproportionately affect low-income communities (and due to 
systematic injustices people of color disproportionately make up low income 
communities). Low-income communities have less resilience to storms and 
environmental crises caused by climate change, so it is important to 
preemptively investigate what communities are most affected by social and
environmental injustices. We believe that education data may highlight many of 
these injustices and we are interested in uncovering some these problems. It is 
critical that we continue uncovering social and environmental injustices to 
protect the health and well-being of all communities.

\  

# Summary Information Script
```{r, include=FALSE}
source("Summary.R")
```
For our summary information, we were interested in highlighting the poverty rates 
and access to education that existed in specific communities. We were also interested 
in learning how an access to education may affect the perspectives of different communities
on environmental issues such as global warming. After calculating the number of different 
school districts, counties, and neighborhoods that our data originated from, we were able to 
dive into the percentage of people who supported environmental topics such as capping CO2 
emissions and teaching children about global warming on a national, state, and county level using
data from the Yale Climate Opinion Maps project. Our data represents 4,563 different locations
across the country. About 61.8% of the national populations supports capping CO2 emissions
while 73% of the population supports teaching about the concept of global warming in schools.
Furthermore, we calculated the average income-to-poverty ratio of the neighborhoods depicted 
in our dataset from the NCES which represents a spectrum of 0-999, the lower numbers 
indicating more impoverished locations. We found that the minimum IPR was 35 while the highest
was 986. We were also able to calculate the average IPR across the U.S. which falls at 293.83
while the poverty line currently stands at an IPR of about 100. 

\  

# Table Script
#```{r}
#source("Table.R")
#```

\  

# Map Chart
\  
```{r map_chart, echo = F, message = F, fig.width = 10}
source("Map Chart.R")
```
The **Comparable Wage Index for Teachers (CWIFT)** is a complex cost index
estimate generated by the National Center for Education Statistics (NCES) to
allow researchers to adjust education finance data for comparison across
geographic regions, down to the per-district level. The CWIFT value for each
school district is an estimate of the cost index for that region, and is
reflective of the cost for the same amount of value from education spending. The
NCES provides CWIFT estimates at the school district level, but this chart shows
the CWIFT estimate per state to help demonstrate the concept.

While these CWIFT numbers are not directly useful to us, and shouldn't tell us
anything we don't already know (more purple states have higher costs of living),
but if we work with any education spending data further into our project, we can
use these CWIFT values to adjust for disparity in dollar value across the
country for more accurate comparisons. For instance, according to the CWIFT
estimates, \$1 of education spending in Idaho buys more total value than \$1 in
Washington. Unsurprisingly, we can see clearly from the chart that California,
Washington, and New York have the highest cost indexes in the country.