---
title: "Exploratory Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
We are studying how educational data highlights social injustices. Variables
such as school amenities, school funding, graduation rate, dropout rate, and 
more could demonstrate what districts are receiving disproportionately high
or low support. We will investigate how primary and secondary education data 
relates to post-secondary (post-graduation) education data.If able, we are also 
interested in analyzing how access to environmental education and outdoor spaces
impacts students post-graduation (such impacts could include belief in climate 
change). Social and environmental justice are connected because the impacts of
climate change disproportionately affect low-income communities (and due to 
systematic injustices people of color disproportionately make up low income 
communities). Low-income communities have less resilience to storms and 
environmental crises caused by climate change, so it is important to 
preemptively investigate what communities are most affected by social and
environmental injustices. We believe that education data may highlight many of 
these injustices and we are interested in uncovering some these problems. It is 
critical that we continue uncovering social and environmental injustices to 
protect the health and well-being of all communities.

\  

# Summary Information Script
```{r}
source("Summary.R")
```

\  

# Table Script
```{r}
source("Table.R")
```

\  

# Map Chart
\  
```{r map_chart, echo = F, message = F, fig.width = 10}
source("Map Chart.R")
```
The **Comparable Wage Index for Teachers (CWIFT)** is a complex cost index
estimate generated by the National Center for Education Statistics (NCES) to
allow researchers to adjust education finance data for comparison across
geographic regions, down to the per-district level. The CWIFT value for each
school district is an estimate of the cost index for that region, and is
reflective of the cost for the same amount of value from education spending. The
NCES provides CWIFT estimates at the school district level, but this chart shows
the CWIFT estimate per state to help demonstrate the concept.

While these CWIFT numbers are not directly useful to us, and shouldn't tell us
anything we don't already know (more purple states have higher costs of living),
but if we work with any education spending data further into our project, we can
use these CWIFT values to adjust for disparity in dollar value across the
country for more accurate comparisons. For instance, according to the CWIFT
estimates, \$1 of education spending in Idaho buys more total value than \$1 in
Washington. Unsurprisingly, we can see clearly from the chart that California,
Washington, and New York have the highest cost indexes in the country.