---
title: "Exploratory Analysis"
output: html_document
---
```{r, include=FALSE}
source("Summary.R")
source("Table.R")
source("Poverty and Technology Chart.R")
source("Map Chart.R")
source("US CLIMATE OPINION.R")
```
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


We are studying how educational data highlights social injustices. Variables
such as school amenities, school funding, graduation rate, dropout rate, and 
more could demonstrate what districts are receiving disproportionately high
or low support. We will investigate how primary and secondary education data 
relates to post-secondary (post-graduation) education data.If able, we are also 
interested in analyzing how access to environmental education and outdoor spaces
impacts students post-graduation (such impacts could include belief in climate 
change). Social and environmental justice are connected because the impacts of
climate change disproportionately affect low-income communities (and due to 
systematic injustices people of color disproportionately make up low income 
communities). Low-income communities have less resilience to storms and 
environmental crises caused by climate change, so it is important to 
preemptively investigate what communities are most affected by social and
environmental injustices. We believe that education data may highlight many of 
these injustices and we are interested in uncovering some these problems. It is 
critical that we continue uncovering social and environmental injustices to 
protect the health and well-being of all communities.
```{r}

```

\  

# Summary Information Script
```{r, echo = FALSE}
summary_info
```

For our summary information, we were interested in highlighting the poverty rates 
and access to education that existed in specific communities. We were also interested 
in learning how an access to education may affect the perspectives of different communities
on environmental issues such as global warming. After calculating the number of different 
school districts, counties, and neighborhoods that our data originated from, we were able to 
dive into the percentage of people who supported environmental topics such as capping CO2 
emissions and teaching children about global warming on a national, state, and county level using
data from the Yale Climate Opinion Maps project. Our data represents 4,563 different locations
across the country. About 61.8% of the national populations supports capping CO2 emissions
while 73% of the population supports teaching about the concept of global warming in schools.
Furthermore, we calculated the average income-to-poverty ratio of the neighborhoods depicted 
in our dataset from the NCES which represents a spectrum of 0-999, the lower numbers 
indicating more impoverished locations. We found that the minimum IPR was 35 while the highest
was 986. We were also able to calculate the average IPR across the U.S. which falls at 293.83
while the poverty line currently stands at an IPR of about 100. 

\  

# Table Script
```{r, echo = FALSE}
EconAgg
```
We decided to include this table on Climate Education because it displays
the amount of approval that specific topics, such as global warning education
or supporting the regulation of CO2 and gas emissions, can be correlated 
to the approval of political factors such as supporting local officials or 
the president. Furthermore, this table reflects how people in different states
and counties may support or oppose certain issues and how this relates to the 
rates of poverty or environmental education in a particular location. 

\  

# Map Chart
\  
```{r, echo = FALSE}
map_chart
```
The **Comparable Wage Index for Teachers (CWIFT)** is a complex cost index
estimate generated by the National Center for Education Statistics (NCES) to
allow researchers to adjust education finance data for comparison across
geographic regions, down to the per-district level. The CWIFT value for each
school district is an estimate of the cost index for that region, and is
reflective of the cost for the same amount of value from education spending. The
NCES provides CWIFT estimates at the school district level, but this chart shows
the CWIFT estimate per state to help demonstrate the concept.

While these CWIFT numbers are not directly useful to us, and shouldn't tell us
anything we don't already know (more purple states have higher costs of living),
but if we work with any education spending data further into our project, we can
use these CWIFT values to adjust for disparity in dollar value across the
country for more accurate comparisons. For instance, according to the CWIFT
estimates, \$1 of education spending in Idaho buys more total value than \$1 in
Washington. Unsurprisingly, we can see clearly from the chart that California,
Washington, and New York have the highest cost indexes in the country.

\

# Poverty and Technology Chart
\  
```{r, echo = FALSE}
computer_poverty
```
The NCES data was used in this chart to compare the percentage of 
households with a computer to the percentage of households under the poverty
line in each district. We analyzed this data by state to look more closely at 
how this data changed based on location. This data shows a general trend in most
cases of districts with a higher percentage of households below the poverty 
level having a lower percentage of households with a computer. In further 
analysis, it would be interesting to see how this data correlated with education
success such as high school or college graduation rates. The purpose of including
the information as seen in the chart is to determine a baseline understanding
of if these two variables correlate, and then we will be able to incorporate a
deeper analysis based off this. We included these specific 9 states to show a 
variety of west coast, east coast, and central states. After looking extensively
through all the states by charting each of them with this data, we chose the 
ones with stronger visible correlation to indicate that there may be a 
relationship  between these variables,but in future analysis we would like to 
include more states to ensure our data is unbiased.

# United States Climate Opinion Chart
\  
```{r, echo = FALSE}
HAPPENING_PLOT
```
The Yale Climate Opinion Maps project collects data about public opinion 
regarding climate belief and policy support. This chart organizes the data by 
state about whether or not climate change is currently happening. It shows that 
the three states that have the highest percentage of climate denial are
North Dakota, West Virginia, and Wyoming. The states with the highest percentage
of climate belief include California, Hawaii, Maryland, and New York. This
information can be used to guide further analysis regarding how funding,
poverty rates, and education in each state can have an effect on climate belief. 
This chart may also suggest how geography can play a role in climate belief. 
Organizing this information by state is also useful for analyzing policy support
and action taken by local governments. A second chart is included that shows 
public opinion by state regarding whether or not global warming should be taught
in schools, to which the states with the highest percent of climate denial
are (not surprisingly) also the states with the highest percent of opposition to 
teaching global warming in schools. Overall, these charts illustrating climate
belief in the United States shows that climate denial can be as high as 25% in 
certain states, as low as 12% in other states, meaning the opinion of the states 
vary by up to 13%. Climate belief should be more consistent across the country, 
and in the future we would like to break down beliefs by county to better 
understand the surrounding factors that may influence climate belief.

```{r, echo = FALSE}
TEACH_PLOT
```